Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2

### 2019-02-13 Thesis_Latex/FinalReport/figure/flowchart/flowchart.tex
update path planning, Paper, Final Report

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=green!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\begin{tikzpicture}[node distance = 3.3cm, auto]
    % Place nodes
    \node [decision] (detection) {Obstacle 
    detected?}; 
    \node [cloud,right of=detection] (start) {Start};
    \node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
	\node [block,left of=detection] (reference) {Follow Path: stick to the lane};
    \node [block,below of=multiObstacles] (distance) {Distance to closest obstacle};
    \node [block,right of=multiObstacles] (distances) {Distance between the obstacles};
    \node [decision,below of=distances](space) {Free Space for Overtaking?};
    \node [block,right of=space](braking){Braking/ Ostacle Velocity};
    \node [block,below of=space](free){Overtaking on free lane};
    \node [decision,below of=distance] (decisionOvertaking) {Left w.r.t vehicle?};
    \node [block, below of=decisionOvertaking] (rightOver) {Right Overtaking};     
    \node [block, left of=decisionOvertaking] (leftOver) {Left Overtaking};

>>>>

	% Define block styles
	\tikzstyle{decision} = [diamond, draw, fill=blue!10, 
	text width=4.5em, text centered, node distance=3cm, inner sep=0pt]
	\tikzstyle{block} = [rectangle, draw, fill=green!10, 
	text width=5em, text centered, rounded corners, minimum height=4em]
	\tikzstyle{line} = [draw, -latex']
	\tikzstyle{cloud} = [draw, ellipse,fill=red!10, node distance=3cm,
	minimum height=2em]

	\begin{tikzpicture}[font={\small\sffamily}, node distance = 3cm, auto, scale=0.75,every node/.style={transform shape}]
	% Place nodes
	\node [decision] (detection) {Obstacle 
		detected?}; 
	\node [cloud,left of=detection] (start) {Start};
	\node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
	\node [block,right of=detection] (reference) {Follow Path: stick to the lane};
	\node [block,left of=multiObstacles] (distance) {Obtain distance to closest obstacle};
	\node [block,right of=multiObstacles] (distances) {Obtain distance between the obstacles};
	\node [decision,below of=distances](space) {Free Space for Overtaking?};
	\node [block,right of=space,node distance=3.3cm](braking){Braking/ Ostacle Velocity};
	\node [block,below of=space](free){Overtaking on free lane};
	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {Left w.r.t vehicle?};
	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Right Overtaking};     
	\node [block, right of=decisionOvertaking] (leftOver) {Left Overtaking};
